Evaluation of probabilistic photometric redshift estimation approaches for \boldblue{ \textsc{The Rubin Observatory Legacy Survey of Space and Time} (LSST)}

### 2020-03-09 paper/tex/introduction.tex
add Wolf 2009 reference and corresponding sentence

To fully characterize such physical degeneracies, subsequent photometric galaxy catalogue data releases, \citep[e.~g.~][]{Sheldon:2012, Erben:2013, de_Jong:17}, provide a more informative \pz\ data product, the \pz\ probability density function (PDF), that describes the redshift probability, commonly denoted as $p(z)$, as a function of a galaxy's redshift, conditioned on the observed photometry.
Early template-based methods such as \citet{Fernandezsoto:99} approximated the likelihood of photometry conditioned on redshift with the relative \chisq\ values of template spectra.
Not long after, Bayesian adaptations of template-based approaches such as \citet{Benitez:00} combined the estimated likelihoods with a prior to yield a posterior PDF of redshift conditioned on photometry.
While the first data-driven \pz\ algorithms yielded a point estimate, \citet{Firth:03} estimated a \pzpdf\ using a neural net with realizations scattered within the photometric errors.

>>>>

To fully characterize such physical degeneracies, subsequent photometric galaxy catalogue data releases, \citep[e.~g.~][]{Sheldon:2012, Erben:2013, de_Jong:17}, provide a more informative \pz\ data product, the \pz\ probability density function (PDF), that describes the redshift probability, commonly denoted as $p(z)$, as a function of a galaxy's redshift, conditioned on the observed photometry.
Early template-based methods such as \citet{Fernandezsoto:99} approximated the likelihood of photometry conditioned on redshift with the relative \chisq\ values of template spectra.
Not long after, Bayesian adaptations of template-based approaches such as \citet{Benitez:00} combined the estimated likelihoods with a prior to yield a posterior PDF of redshift conditioned on photometry.
While the first data-driven \pz\ algorithms yielded a point estimate, \citet{Firth:03} estimated a \pzpdf\ using a neural net with realizations scattered within the photometric errors.  \boldblue{Several years later \citet{Wolf:09} used a data driven $\chi^{2}$ approach to estimate redshift PDFs, and specifically noted an intrinsic floor in redshift uncertainties even under ideal conditions can arise due to the intrinsic spread of redshifts within the training set even in well localized regions of parameter space.}
